Testing the precision of Bangla Communication Scale: Item Response Theory Guided Analysis

### 2022-02-01 manuscript.Rmd
yml header updated

author: 
  - name          : "Nusrat Jahan"
    affiliation   : "1, *"
    role:         
      - Conceptualization
      - Project Management

      - Data Curation
      - Writing - Original Draft Preparation

    - name          : "Mushfiqul Anwar Siraji"
    affiliation   : "2, *"
    role:
      - Conceptualization
      - Project Management
      - Formal Analysis
      - Data Visualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing

    - name          : "Zinnatul Boraka"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Department of Educational and Counselling Psychology,University of Dhaka,Dhaka 1000"
    email         : "my@email.com"
    role:
      - Conceptualization
      - Writing - Review & Editing

@@

bibliography      : ["references.bib"]

@@

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---
```{r setup, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = F, message = F, dpi=1200)

@@

```{r pacman, eval=FALSE, include=FALSE}
#You need to run this chunk 1X in your system 
#install.packages("pacman")#Run this if you don't have pacman installed.
pacman::p_load(MOTE, tidyverse, psych, lavaan,kableExtra,gt,gtsummary, mirt,likert,kutils,semPlot,semTable,semTools,ggcorrplot,dlookr,qgraph,paran,EFA.MRFA,VIM,DiagrammeR,DiagrammeRsvg,ggplot2,cowplot,rsvg,questionr,magick, simsem,readxl, stringr,RColorBrewer,WrightMap, foreign,DT,SimDesign)
pacman::p_install_gh("jthomasmock/gtExtras")
pacman::p_install_gh("crsh/papaja")
pacman::p_install_gh("masiraji/tabledown")
pacman::p_install_gh("crsh/citr")

@@

```{r library, eval=FALSE, include=FALSE}
#This chunk holds code for calling the required packages

@@

---
nocite: |
  `r cite_r("references.bib")`

@@

# Methods
```{r data, include=F}
# data <- readxl::read_excel("Processeddata/communication_data_n_582.xlsx")
# readr::write_rds(data, "Processeddata/communication_data_n_582.rds")
data <- readr::read_rds("Processeddata/communication_data_n_582.rds")

@@

irt.data <- sem.data[,2:24]

@@

```{r descriptivrd, eval=FALSE, include=FALSE}
desc <- data[,c(3, 5,6)]
## Recoding desc$Sex
desc$Sex <- fct_recode(desc$Sex,
  "Boy" = "male",
  "Girl" = "female"
)
colnames(desc) <- c("Gender", "Social Status", "Age")

    missing = "no"
    ) %>% add_overall() %>% bold_labels() %>% 
modify_header(label ~ "**Variable**")  %>%
  modify_caption("Demographic Characteristics") 
```

```{r gt-pic, include=F}
des_tab  %>%    # build gtsummary table
  as_gt() %>%             # convert to gt table
  gt::gtsave(             # save table as image
    filename = "Figures/demographics.png"
  )
```

```{r}
reliability <- psych::alpha(com2, check.keys = T)
```

>>>>

author: 
  - name          : "Nusrat Jahan"
    affiliation   : "1"
    corresponding : no    # Define only one corresponding author
    role:         
      - Conceptualization
      - Data Curation
      - Writing - Original Draft Preparation
  - name          : "Mushfiqul Anwar Siraji"
    affiliation   : "2"
    corresponding : no   # Define only one corresponding author
    address       : "Monash University Malaysia,Jalan Lagoon Selatan, 47500 Bandar Sunway,Selangor Darul Ehsan, Malaysia."
    email         : "mushfiqul.anwarsiraji@moansh.edu"
    role:
      - Conceptualization
      - Project Management
      - Formal Analysis
      - Data Visualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing

  - name          : "Zinnatul Borak"
    affiliation   : "1"
    corresponding : yes   # Define only one corresponding author
    address       : "Department of Educational and Counselling Psychology,University of Dhaka,Dhaka 1000"
    email         : "mushfiqul.anwarsiraji@moansh.edu"
    role:
      - Conceptualization
      - Writing - Review & Editing

@@

bibliography      : ["r-references.bib", "references.bib"]

@@

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = F, message = F, dpi=1200)

@@

```{r pacman, eval=FALSE, include=FALSE}
#You need to run this chunk 1X in your system 
#install.packages("pacman")#Run this if you don't have pacman installed.
pacman::p_load(MOTE, tidyverse, psych, lavaan,kableExtra,gt,gtsummary, mirt,likert,kutils,semPlot,semTable,semTools,ggcorrplot,dlookr,qgraph,paran,EFA.MRFA,VIM,DiagrammeR,DiagrammeRsvg,ggplot2,cowplot,rsvg,questionr,magick, simsem,readxl, stringr,RColorBrewer,WrightMap, foreign,DT,SimDesign)
library(papaja)
pacman::p_install_gh("jthomasmock/gtExtras")
pacman::p_install_gh("crsh/papaja")
pacman::p_install_gh("masiraji/tabledown")
pacman::p_install_gh("crsh/citr")

@@

```{r library,include=FALSE}
#This chunk holds code for calling the required packages

@@

---
nocite: |
  `r papaja::cite_r("references.bib")`

@@

# Study 1: Translations and Factor Structure

Our first study had two objectives. First, we translated the English communication scale to Bangla language. Second, to identified the latent structure of the Bangla Communication Scale (BCS) using Exploratory Factor Analysis (EFA)

## Methods

```{r data, include=F}
# data <- readxl::read_excel("Processeddata/communication_data_n_582.xlsx")
# readr::write_rds(data, "Processeddata/communication_data_n_582.rds")
data <- readr::read_rds("Processeddata/communication_data_n_582.rds")

@@

irt.data <- sem.data[,2:24]
```

```{r sescrptives, include=FALSE}
desc <- efa.data.full[,c(3,4,5)]
## Recoding desc$Sex
desc$Gender <- fct_recode(desc$Gender,
  "Boy" = "male",
  "Girl" = "female"
)
colnames(desc) <- c("Gender", "Age", "Socio Economic Status")

    missing = "no"
    ) %>% add_overall() %>% bold_labels() %>% 
modify_header(label ~ "**Variable**")  %>%
  modify_caption("Demographic Characteristics")

as_tibble(des_tab) -> desc_tibble 
as_kable_extra(des_tab, format = "latex",booktabs = T) -> desc_kable #save it as a knitr::kable

des.2 <- desc %>% 
  psych::describeBy("Gender")
female <- as.tibble(des.2$Female)
male <- as.tibble(des.2$Male)

@@

A cross-sectional survey was used to collect data from a large sample of students of grade 8-10 (n = `r nrow(efa.data)`) from ---- schools following convenience sampling method. T. For estimating the sample size for the CFA we followed the N:q rule [@RN1268; @RN1269; @RN1270; @RN1271] where 10 participants per parameters is required to earn trustworthiness of the result. Our sample size exceeds the requirement. Among `r nrow(data)` participants, `r female[1,2]` were female aged between `r female[4,8]` to `r female[4,9]` years (`r round(female[4,3],2)`±`r round(female[4,4],2)`). `r male[1,2]`  were male with an age range between `r male[4,8]` to `r male[4,9]` years (`r round(male[4,3],2)`±`r round(male[4,4],2)`). Table \@ref(tab:demographics) summarizes the demographics.
